<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Put the title of your vignette here}
-->

---
title: "catPkg"
author: "me"
date: "12/7/2014"
output:
  pdf_document:
    keep_tex: yes
---


```{r setup, cache=FALSE, include=FALSE}
library(knitr)
opts_chunk$set(eval = FALSE)
#output <- opts_knit$get("rmarkdown.pandoc.to")
#if (output=="html") opts_chunk$set(fig.width=11, fig.height=11)
#if (output=="docx") opts_chunk$set(fig.width=6,  fig.height=6)
```

(http://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/)

```{r}
# install.packages("devtools")
library("devtools")
# devtools::install_github("klutometis/roxygen")
library(roxygen2)
packageDescription("roxygen2")

# setwd("parent_directory")
# create("cats")
```
## Step 1: Create your package directory
```{r, eval = FALSE}
setwd("parent_directory")
create("cats")
```

```{r, eval = FALSE}
cat_function <- function(love = TRUE){
    if(love==TRUE){
        print("I love cats!")
    }
    else {
        print("I am not a cool person.")
    }
}
# There are three main ways to run roxygen:
#     Ctrl + Shift + D, if you're using RStudio.
devtools::document()
roxygen2::roxygenise()
```

### Step 4: Process your documentation
Now you need to create the documentation from your annotations earlier. You've already done the 'hard' work in Step 3. Step 4 is as easy doing this:
```{r, eval = FALSE}
# setwd("./cats")
# > getwd()
# [1] "/home/rstudio/pkg/catPkg"
document()
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the echo = FALSE parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## (Bonus) Step 6: Make the package a GitHub repo
This is not a post about learning to use git and GitHub - for that I recommend Karl Broman's Git/GitHub Guide. The benefit, however, to putting your package onto GitHub is that you can use the devtools install_github() function to install your new package directly from the GitHub page.

```{rsdfsd, eval=FALSE} 
# f
install_github('JohnGavin/catPkg')
```
